Physcraper: A Python package for continually updated gene trees

### 2020-05-23 phylota-overview.Rmd
phylota citations 101-110

    compare the performance of SUMAC to Phylota.

@@

    to parallelize BLAST [@yong2010screening], as well as @gao2011solution, @li2013partfasttree, and @meng2014rapidtree, all
    cite phylota using the exact same phrase, as one among other "studies based on data mining large numbers of taxa or loci".

@@

1. When the software was actually used to construct (partially or in full) a DNA

@@

    and wrynecks) [@dufort2016augmented], augmented with data from an updated GenBank

@@

1. When the website was used to identify sequences and markers available in

@@

1. Sometimes, it was cited by mistake:

@@

1. When phylota was used to extract full trees (not only DNA data sets or markers):

>>>>

    compare the performance of SUMAC to Phylota. This is also presented in their PhD dissertation [@freyman2017phylogenetic].

@@

    to parallelize BLAST [@yong2010screening], as well as @gao2011solution, @li2013partfasttree,
    @meng2015sotree, and @meng2014rapidtree, all cite phylota using the exact same
    introduction and sentence: as one among other "studies based on data mining large numbers of taxa or loci".

@@

    - @mahmood2015avian PhD dissertation presents a database of avian Raptor sequences
    (raptorbase), based on the phylota pipeline.
    - @ruiz2019datataxa develops datataxa and cite phylota as "software that has
    been developed to mine the massive amount of information stored in GenBank", along with its R version [phylotaR; @bennett2018phylotar] and restez <https://www.rdocumen-tation.org/packages/restez/versions/1.0.0>.
2. When the software was actually used to construct (partially or in full) a DNA

@@

    and wrynecks) [@dufort2016augmented; @dufort2015coexistence], augmented with data from an updated GenBank

@@

    - @freyman2015sumac [also in @freyman2017phylogenetic], use phylota to construct
    a phylogeny (or maybe only mine genbank???) of the Onagraceae and Lythracea,
    and compare it to the tool they propose, SUMAC.
    - @blackmon2017synthesis PhD study applies phylota to reconstruct a 822 mite
    species tree.
    - A study of the effect of poliploidy on niche evolution [@baniaga2018polyploid],
    uses phylota to get a DNA data set for 132 unique taxa of vascular plants from
    16 families and 25 genera,and a tree of 33 genera from 20 different families
    comprising 1706 taxa.
3. When the website was used to identify sequences and markers available in

@@

4. Sometimes, it was cited by mistake:

@@

5. When phylota was used to extract full trees (not only DNA data sets or markers):
